Efficiency

### 2018-09-20 Second.Rnw
with the crucial float barriers

@@

@@

\section{The weight and size argument}
Both Dr David Kershaw, Chief of Maritime Division at DSTG\parencite{kerr2018}, as well as Mr Brent Clark\parencite{clark2018} have both made arugments to the effect of suggesting that it was the Australian submarine's very large size which is what made the pumpjet viable, where it might not be for smaller submarines.  I responded directly to Clark's comments arguing that the size necessitated by the extra fuel and batteries a pumpjet demanded could hardly be counted as an advantage \parencite{morrison2018b}.  However, Dr Kershaw's argument reveals a different takon on why size is important.  His comments make it clear that it is actually the large weight of the pumpjet \textit{itself} rather than the additional fuel and batteries it required, that was significant.

@@

@@

\section{Discussion}
Having given due consideration to the three signiciant arguments that have been made in response to my paper, one can only conclude that either a degree of incompetence hitherto unthinkeable pervades defence, or alternatively the arguments are disingenuous.

@@

\newpage
\subsection{Answer to Question on Notice}\label{QON148}

\begin{figure}[h]
\includegraphics[width=0.8\textwidth, center]{QON148.png}
\end{figure}

\newpage
\subsection{Answer to Question on Notice}\label{QON150}

@@

\newpage
\subsection{Answer to Question on Notice}\label{QON151}
\begin{figure}[h]
\includegraphics[width=0.7\textwidth, center]{QON151.png}
\end{figure}

@@

\newpage
\subsection{Answer to Question on Notice}\label{QON1}
\begin{figure}[h]
\includegraphics[width=0.7\textwidth, center]{QON1.png}
\end{figure}

\newpage
\subsection{Answer to Question on Notice}\label{QON2}
\begin{figure}[h]
\includegraphics[width=0.7\textwidth, center]{QON2.png}
\end{figure}

\newpage
\subsection{Answer to Question on Notice}\label{QON3}
\begin{figure}[h]
\includegraphics[width=0.7\textwidth, center]{QON3.png}
\end{figure}

\newpage
\subsection{Hansard Extract, Senate Economic References Committee Public Hearing - 7th June 2018 \cite{SEN2018morrison}}\label{SENmorrison}

>>>>

\usepackage{placeins}

@@

\FloatBarrier

@@

\FloatBarrier

\section{The weight and size argument}

Both Dr David Kershaw, Chief of Maritime Division at DSTG\parencite{kerr2018}, as well as Mr Brent Clark\parencite{clark2018} have both made arugments to the effect of suggesting that it was the Australian submarine's very large size which is what made the pumpjet viable, where it might not be for smaller submarines.  I responded directly to Clark's comments arguing that the size necessitated by the extra fuel and batteries a pumpjet demanded could hardly be counted as an advantage \parencite{morrison2018b}.  However, Dr Kershaw's argument reveals a different takon on why size is important.  His comments make it clear that it is actually the large weight of the pumpjet \textit{itself} rather than the additional fuel and batteries it required, that was significant.

@@

\begin{tcolorbox}[width=0.9\textwidth, center, colback=green!5!white,colframe=green!75!black, title= \textbf{How a scientist feels being told that the pumpjet is a gamechanger for our diesel-electric submarine because it is so large, where it wouldn't make sense on a smaller one}]

Bruce: I'm not sure about using these fat nobbly tires on my road-bike for the cycle tour... No-one else is using such tyres on a road-bike, I think they'd be slow and inefficient.

James: Don't be silly!  Everyone else would love to use fat nobbly tyres on a road-bike, the only reason they can't is that those cyclists themselves are just so slim and athletic, and can't use the nobbly fat nobbly tyes. Bruce, don't you realise that you're the \textit{only} cyclist every attempting this tour who weights 200kg, roughly three times what most road-cyclistst weigh? If a 70kg rider attempted those speeds with fat knobbly tyres, they wouldn't have the weight to stabilise the forces involved, and they'd be thrown off their bicycle in a catastophic crash which would probably be fatal.  But for fat cyclists such as yourself, fat nobbly tires are a real game-changer!

Bruce:  What about that one lonely guy over there riding on fat knobbly tyres.  He looks like he weighs about 70kg, and he's not having a catastopic crash, he's just going really slow and looks tired.  Maybe that's why he's sticking to the footpath.

James: Oh...

Bruce: And didn't you also tell me that you tried riding with fat nobbly tires once years ago?  How did you survive the catastophic crash?

\FloatBarrier

@@

\FloatBarrier

\section{Discussion}

@@

\subsection{Answer to Question on Notice}\label{QON148}

\begin{figure}[h]
\includegraphics[width=0.7\textwidth, center]{QON148.png}
\end{figure}

\subsection{Answer to Question on Notice}\label{QON150}

@@

\subsection{Answer to Question on Notice}\label{QON151}

\begin{figure}[h]
\includegraphics[width=0.7\textwidth, center]{QON151.png}
\end{figure}

@@

\subsection{Answer to Question on Notice}\label{QON1}

\begin{figure}[h]
\includegraphics[width=0.7\textwidth, center]{QON1.png}
\end{figure}

\subsection{Answer to Question on Notice}\label{QON2}

\begin{figure}[h]
\includegraphics[width=0.7\textwidth, center]{QON2.png}
\end{figure}

\subsection{Answer to Question on Notice}\label{QON3}

\begin{figure}[h]
\includegraphics[width=0.7\textwidth, center]{QON3.png}
\end{figure}

\subsection{Hansard Extract, Senate Economic References Committee Public Hearing - 7th June 2018 \cite{SEN2018morrison}}\label{SENmorrison}
